Concurrent Programming with CXL

### 2020-06-17 book/paper.tex
Latest

\section*{Exercises}
\begin{enumerate}
\item See what happens if, instead of initializing \texttt{result} to 0,
you initialize it to 1.  (You do not need to understand the error report at this time.)
\item Write a CXL program that computes squares by repeated adding.  So the program
should compute the square of $x$ by adding $x$ to an initial value of 0 $x$ times.
\end{enumerate}

@@

Hopefully you have started thinking of how to solve the concurrency
problem and you may already have prototyped some solutions.
In this chapter we will go through a few reasonable but broken attempts.
At the heart of the problem is that we would like make sure that, when
the \texttt{count} variable is being updated, no other process is
trying to do the same thing.  This is called a \emph{critical section}
(aka critical region)~\cite{EWD123}:
\index{critical section}
\glsadd{critical section}
\index{critical region}
a set of instructions where only one process is allowed to execute at a
time.

>>>>

\section*{Exercises}
\begin{enumerate}
\item See what happens if, instead of initializing \texttt{result} to 0,
you initialize it to 1.  (You do not need to understand the error report at this time.)
Explain in English what the problem is.
\item Write a CXL program that computes squares by repeated adding.  So the program
should compute the square of $x$ by adding $x$ to an initial value of 0 $x$ times.
\end{enumerate}

@@

Hopefully you have started thinking of how to solve the concurrency
problem and you may already have prototyped some solutions.
In this chapter we will go through a few reasonable but broken attempts.
At the heart of the problem is that we would like make sure that, when
the \texttt{count} variable is being updated, no other process is
trying to do the same thing.  This is called a \emph{critical section}
(aka critical region)~\cite{EWD123}:
a set of instructions where only one process is allowed to execute at a
time.
\index{critical section}
\index{critical region}
\glsadd{critical section}
